DATA 621 – Business Analytics and Data Mining: Homework #1

### 2020-09-10 HW1/HW1_BP.rmd
Update HW1_BP.rmd

train_set <- read.csv('/Users/Bryan/Documents/Data 621/HW 1/moneyball-training-data.csv')
eval_set <- read.csv('/Users/Bryan/Documents/Data 621/HW 1/moneyball-evaluation-data.csv')

>>>>

train_set <- read.csv('https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/HW1/data/moneyball-training-data.csv')
eval_set <- read.csv('https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/HW1/data/moneyball-evaluation-data.csv')
